### 2022-05-12 manuscript/manuscript.Rmd
IQR changed to lower and upper quartiles

layout <- '
AAABC
DEFGH
IJKLM
OPQRS
TUVWX
'
#Plot
megaPlot <- wrap_plots(
  A = allfieldsPlot, 
  B = all_field_plots[[1]],
  C=all_field_plots[[2]],
  D=all_field_plots[[3]], 
  E=all_field_plots[[4]], 
  F=all_field_plots[[5]], 
  G=all_field_plots[[6]], 
  H=all_field_plots[[7]], 
  I=all_field_plots[[8]], 
  J=all_field_plots[[9]],
  K=all_field_plots[[10]],
  L=all_field_plots[[11]],
  M=all_field_plots[[12]],
  O=all_field_plots[[13]],
  P=all_field_plots[[14]],
  Q=all_field_plots[[15]],
  R=all_field_plots[[16]],
  S=all_field_plots[[17]],
  T=all_field_plots[[18]],
  U=all_field_plots[[19]],
  V=all_field_plots[[20]],
  W=all_field_plots[[21]],
  X=all_field_plots[[22]],
  design = layout) & 
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) # Remove axis labels from all

@@

pppr_types_numeric_limits <- pppr_types_numeric_limits %>%
  group_by(PPPR_name_harmonized) %>% # summarise by pppr type
  summarise(
    across(c(wordLimits, timeLimits, referenceLimits), 
           list(median = median,
               IQR = IQR), 
           na.rm = T)) %>%
  bind_rows( # attached overall summary
    pppr_types_numeric_limits %>%
      summarise(
    across(c(wordLimits, timeLimits, referenceLimits), 
           list(median = median,
               IQR = IQR), 
           na.rm = T)) %>%
      mutate(PPPR_name_harmonized = "All types")
  )

pppr_types_tab <- pppr_types %>%
  left_join(pppr_types_freq, by = 'PPPR_name_harmonized') %>%
  left_join(pppr_types_numeric_limits, by = 'PPPR_name_harmonized') %>%
  mutate(
    length_n_percent = paste0(hasLengthLimit,' (',round(hasLengthLimit/n*100,0),'%)'),
    length_quant_n_percent = paste0(hasLengthLimit_quant,' (',round(hasLengthLimit_quant/n*100,0),'%)'),
    length_md_iqr = paste0(wordLimits_median,' (',wordLimits_IQR,')'),
    time_n_percent = paste0(hasTimeLimit,' (',round(hasTimeLimit/n*100,0),'%)'),
    time_quant_n_percent = paste0(hasTimeLimit_quant,' (',round(hasTimeLimit_quant/n*100,0),'%)'),
    time_md_iqr = paste0(round(timeLimits_median,0),' (',round(timeLimits_IQR,0),')'),
    ref_n_percent = paste0(hasRefLimit,' (',round(hasRefLimit/n*100,0),'%)'),
    ref_quant_n_percent = paste0(hasRefLimit_quant,' (',round(hasRefLimit_quant/n*100,0),'%)'),
    ref_md_iqr = paste0(referenceLimits_median,' (',referenceLimits_IQR,')'),
    review_n_percent = paste0(hasPeerReview,' (',round(hasPeerReview/n*100,0),'%)')
  ) %>%
  select(`PPPR type` = PPPR_name_harmonized,
         n,
         length_n_percent,
         length_quant_n_percent,
         length_md_iqr,
         time_n_percent,
         time_quant_n_percent,
         time_md_iqr,
         ref_n_percent,
         ref_quant_n_percent,
         ref_md_iqr,
         review_n_percent)
```

@@

```{r fig-practice-prev, fig.width = 7.5, fig.height = 6, fig.path = 'figs/', fig.cap = 'Primary (Panel A) and secondary (Panel B) prevalence estimates for the use of PPPR in all journals overall (N = 330 journals; black diamond, error bars represent 95% confidence intervals) and then in descending order by each scientific domain (n = 15 journals; coloured circles). Domain abbreviations: Agricultural Sciences (AGRI), Biology & Biochemistry (BIO), Chemistry (CHEM), Clinical Medicine (MED), Computer Science (COMSCI), Economics & Business (ECON), Engineering (ENGIN), Environment & Ecology (ECO), Geosciences (GEO), Immunology (IMMUN), Materials Science (MATSCI), Mathematics (MATH), Microbiology (MICBIO), Molecular Biology & Genetics (MOLBIO), Multidisciplinary (MULTI), Neuroscience & Behavior (NEURO), Pharmacology & Toxicology (PHARM), Physics (PHYS), Plant & Animal Science (PLANT), Psychiatry & Psychology (PSY), Social Sciences (SOCSCI), Space Science (SPACE).'}
plt1 + plt2
```

>>>>

layout <- '
AAABC
DEFGH
IJKLM
OPQRS
TUVWX
'

#Plot
megaPlot <- wrap_plots(
  A = allfieldsPlot, 
  B = all_field_plots[[1]],
  C=all_field_plots[[2]],
  D=all_field_plots[[3]], 
  E=all_field_plots[[4]], 
  F=all_field_plots[[5]], 
  G=all_field_plots[[6]], 
  H=all_field_plots[[7]], 
  I=all_field_plots[[8]], 
  J=all_field_plots[[9]],
  K=all_field_plots[[10]],
  L=all_field_plots[[11]],
  M=all_field_plots[[12]],
  O=all_field_plots[[13]],
  P=all_field_plots[[14]],
  Q=all_field_plots[[15]],
  R=all_field_plots[[16]],
  S=all_field_plots[[17]],
  T=all_field_plots[[18]],
  U=all_field_plots[[19]],
  V=all_field_plots[[20]],
  W=all_field_plots[[21]],
  X=all_field_plots[[22]],
  design = layout) & 
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) # Remove axis labels from all

@@

pppr_types_numeric_limits <- pppr_types_numeric_limits %>%
  group_by(PPPR_name_harmonized) %>% # summarise by pppr type
  summarise(
    across(c(wordLimits, timeLimits, referenceLimits), 
           list(median = median,
               IQR = ~ paste0(quantile(.x,na.rm=T)[2],'-',quantile(.x,na.rm=T)[4])), 
           na.rm = T)) %>%
  bind_rows( # attached overall summary
    pppr_types_numeric_limits %>%
      summarise(
    across(c(wordLimits, timeLimits, referenceLimits), 
           list(median = median,
               IQR = ~ paste0(quantile(.x,na.rm=T)[2],'-',quantile(.x,na.rm=T)[4])), 
           na.rm = T)) %>%
      mutate(PPPR_name_harmonized = "All types")
  )

pppr_types_tab <- pppr_types %>%
  left_join(pppr_types_freq, by = 'PPPR_name_harmonized') %>%
  left_join(pppr_types_numeric_limits, by = 'PPPR_name_harmonized') %>%
  mutate(
    length_n_percent = paste0(hasLengthLimit,' (',round(hasLengthLimit/n*100,0),'%)'),
    length_quant_n_percent = paste0(hasLengthLimit_quant,' (',round(hasLengthLimit_quant/n*100,0),'%)'),
    length_md_iqr = paste0(wordLimits_median,' (',wordLimits_IQR,')'),
    time_n_percent = paste0(hasTimeLimit,' (',round(hasTimeLimit/n*100,0),'%)'),
    time_quant_n_percent = paste0(hasTimeLimit_quant,' (',round(hasTimeLimit_quant/n*100,0),'%)'),
    time_md_iqr = paste0(round(timeLimits_median,0),' (',timeLimits_IQR,')'),
    ref_n_percent = paste0(hasRefLimit,' (',round(hasRefLimit/n*100,0),'%)'),
    ref_quant_n_percent = paste0(hasRefLimit_quant,' (',round(hasRefLimit_quant/n*100,0),'%)'),
    ref_md_iqr = paste0(referenceLimits_median,' (',referenceLimits_IQR,')'),
    review_n_percent = paste0(hasPeerReview,' (',round(hasPeerReview/n*100,0),'%)')
  ) %>%
  select(`PPPR type` = PPPR_name_harmonized,
         n,
         length_n_percent,
         length_quant_n_percent,
         length_md_iqr,
         time_n_percent,
         time_quant_n_percent,
         time_md_iqr,
         ref_n_percent,
         ref_quant_n_percent,
         ref_md_iqr,
         review_n_percent)
```

@@

```{r fig-practice-prev, fig.width = 7.5, fig.height = 6, fig.path = 'figs/', fig.cap = 'Primary (Panel A) and secondary (Panel B) prevalence estimates for the use of PPPR in all journals overall (N = 330 journals; black diamond, error bars represent 95% confidence intervals) and then in descending order by each scientific domain (n = 15 journals; coloured circles). Domain abbreviations: Agricultural Sciences (AGRI), Biology & Biochemistry (BIO), Chemistry (CHEM), Clinical Medicine (MED), Computer Science (COMSCI), Economics & Business (ECON), Engineering (ENGIN), Environment & Ecology (ECO), Geosciences (GEO), Immunology (IMMUN), Materials Science (MATSCI), Mathematics (MATH), Microbiology (MICBIO), Molecular Biology & Genetics (MOLBIO), Multidisciplinary (MULTI), Neuroscience & Behavior (NEURO), Pharmacology & Toxicology (PHARM), Physics (PHYS), Plant & Animal Science (PLANT), Psychiatry & Psychology (PSY), Social Sciences (SOCSCI), Space Science (SPACE).'}
plt1 + plt2
```
```{r}
#### FOR SLIDES

# policySummary <- policySummary %>% 
#   mutate(
#     field_abbr = case_when( # create abbreviated field labels to use in figures
#       field == "AGRICULTURAL SCIENCES" ~ "AGRI",
#       field == "BIOLOGY & BIOCHEMISTRY" ~ "BIO",       
#       field == "CHEMISTRY" ~ "CHEM" ,                   
#       field == "CLINICAL MEDICINE" ~ "MED",           
#       field == "COMPUTER SCIENCE" ~ "COMSCI",             
#       field == "ECONOMICS & BUSINESS" ~ "ECON",         
#       field == "ENGINEERING" ~ "ENGIN",                  
#       field == "ENVIRONMENT & ECOLOGY" ~ "ECO",         
#       field == "GEOSCIENCES" ~ "GEO",                  
#       field == "IMMUNOLOGY" ~ "IMMUN",                   
#       field == "MATERIALS SCIENCE" ~ "MATSCI",            
#       field == "MATHEMATICS" ~ "MATH",                
#       field == "MICROBIOLOGY" ~ "MICBIO",                 
#       field == "MOLECULAR BIOLOGY & GENETICS" ~ "MOLBIO", 
#       field == "MULTIDISCIPLINARY" ~ "MULTI",            
#       field == "NEUROSCIENCE & BEHAVIOR" ~ "NEURO",     
#       field == "PHARMACOLOGY & TOXICOLOGY" ~ "PHARM",    
#       field == "PHYSICS" ~ "PHYS",                     
#       field == "PLANT & ANIMAL SCIENCE" ~ "PLANT",       
#       field == "PSYCHIATRY & PSYCHOLOGY" ~ "PSY",       
#       field == "SOCIAL SCIENCES" ~ "SOCSCI",     
#       field == "SPACE SCIENCE" ~ "SPACE",
#       field == "ALL DOMAINS" ~ "OVERALL" 
#   ))
# 
# field_abbr_order <- policySummary %>% filter(field_abbr != "OVERALL") %>% arrange(percent) %>% pull(field_abbr)
# 
# plt <- policySummary %>%
#   mutate(field_abbr = factor(field_abbr, levels = c(field_abbr_order, "OVERALL"))) %>%
#   ggplot(aes(x=field_abbr, y = percent, fill = field_abbr)) +
#   #ylim(0,40) +
#   geom_segment(aes(xend=field_abbr, y=0, yend=percent), colour = 'white') +
#   geom_segment(aes(xend=field_abbr, y=0, yend=percent), colour = 'black', data = . %>% filter(field_abbr != 'OVERALL')) +
#   geom_point(size = 5, shape = 21, colour = 'black', data = . %>% filter(field_abbr != 'OVERALL')) + 
#   geom_segment(aes(xend=field_abbr, y=0, yend=percent), colour = 'black', data = . %>% filter(field_abbr == 'OVERALL')) +
#   geom_point(size = 5, shape = 21, fill = 'black', colour = 'black', data = . %>% filter(field_abbr == 'OVERALL')) + 
#   ylab('journals (%)') +
#   xlab('discipline') +
#   scale_fill_domains() +
#   theme_apa() +
#   theme(
#     panel.grid.major.x = element_line(linetype = 'dashed'),
#     panel.grid.major.y = element_blank(),
#     legend.position = 'none') +
#   coord_flip()
# 
# ggsave(plot = plt, filename = 'slideFig1.png', width = 4, height = 6)
####
```
